Validation of marker gene expression

### 2025-09-15 analyses/cell-type-consensus/template-notebooks/marker-gene-validation.Rmd
change back directory for CI

---
title: "Validation of marker gene expression"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  project_id: "SCPCP000001"
---

@@

# path to results directory
results_dir <- file.path(module_base, "results", "cell-type-consensus", params$project_id)
```

@@

# make dotplot with marker gene exp
dotplot <- ggplot(dotplot_df, aes(y = forcats::fct_rev(y_label), x = gene_symbol, color = mean_exp, size = percent_exp)) +
  geom_point() +
  scale_color_viridis_c(option = "magma") +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  ) +
  labs(
    x = "",
    y = "Broad cell type annotation",
    color = "Mean gene expression",
    size = "Percent cells expressed"
  )

>>>>

---
title: "Validation of marker gene expression"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  project_id: "SCPCP000006"
---

@@

# path to results directory
results_dir <- file.path(module_base, "..", "..", "data", "current", "results", "cell-type-consensus", params$project_id)
```

@@

# make dotplot with marker gene exp
dotplot <- ggplot(dotplot_df, aes(y = forcats::fct_rev(y_label), x = gene_symbol, color = mean_exp, size = percent_exp)) +
  geom_point() +
  scale_color_viridis_c(option = "magma") +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
  ) +
  labs(
    x = "",
    y = "Broad cell type annotation",
    color = "Mean gene expression",
    size = "Percent cells expressed"
  )
